\documentclass[12pt]{CVformat}

\userinformation{ % Set the content that goes into the sidebar of each page
    \begin{flushleft}
        % Comment out this figure block if you don't want a photo
        {\Huge\color{mainblue}Anthony Tanner} \\ % Your name
        \SmallSep
        \url{anthony.tanner12@gmail.com} \\ % Your email address
        07449868688 \\ % Your phone number
        \Sep % Some whitespace
        \profilesection{Skills}
        \begin{itemize}
            \item Teamwork : working with a number of people on large scale projects.
            \item Communication : leading technical discussions on resolving roadblocks within a project.
            \item Agile project management : daily and weekly meetings with my team to ensure progress on a timeline is maintained.
            \item Analytical thinking : debugging of obscure errors requiring breaking down and eliminating of potential causes over a large range of components.
        \end{itemize}
        \Sep
        \profilesection{Technical Skills}
        \begin{itemize}
            \item Linux Operating Systems
            \item Embedded Systems
            \item Use of build systems inc. Yocto (for kernel building) and CMake (compiling large-scale C++ applications)
            \item Git and continuous integration environments
            \item Bash Scripting
            \item Web Technologies
        \end{itemize}
        \Sep % Some whitespace
        \profilesection{Programming Languages}
        \begin{itemize}
            \item C/C++
            \item Java
            \item Haskell
            \item Python
            \item C\#
            \item JavaScript
        \end{itemize}
        \vfill % Whitespace under this block to push it up under the photo
    \end{flushleft}
}

\begin{document}   

    \userinformation 

    \framebreak

    \begin{staticcontents}{1}
        \hfill
        \tikz{\draw[loosely dotted,color=RoyalBlue,line width=1.5pt,yshift=0](0,0) -- (0,\textheight);}
        \hfill\mbox{}
    \end{staticcontents}

    \CVHeading{Personal Statement}
    I am a reliable, hard-working, conscientious individual. I can work in a team or independently. Following my placement, I have experience working with embedded systems and learning new platforms quickly. I am confident tackling new challenges and technologies I have never seen before. I look forward to working in an exciting environment on interesting, new projects.
    \SmallSep

    \CVHeading{Experience}

    \CVItem{Intel (July 2021 - August 2022)}{\textbf{Video \& Vision FPGA Software Engineer} \\
    Responsibilities:
    \begin{itemize}
        \item Expanding functionality of toolkits for providing UIs to video processing projects.
        \item Designing specialized operating systems for projects, enabling and disabling features using the Yocto build system.
        \item Debugging kernel drivers, software and hardware read/write transactions.
        \item Creating a new automation process for creating release packages for multiple projects.
        \item Ensuring software legal compliance on systems releases.
        \item Collaborating with multiple teams of different disciplines to integrate different platforms.
    \end{itemize}}

    \CVItem{Jefferies Solicitors Limited (April 2020 - May 2020)}{\textbf{Administrative Assistant}\\
    I worked managing post for the solicitors, ensuring letters were correctly identified and assigned.}

    \CVItem{Boots (June 2019 - September 2019)}{\textbf{Customer Advisor} \\
    As a part of Boots, I worked within the store to deal with customer needs and organising stock both in the store and the stock room.}
    
    \SmallSep

    \CVHeading{Education}
    
    \CVItem{Univeristy of Birmingham (2019-)}{\textbf{B.Sc. Computer Science with an Industrial Year} \\
    Expected 1st Class with Honours \\
    Key completed modules:
    \begin{itemize}
        \item Artificial Intelligence 2 : 77\%
        \item Security and Networks : 82\%
        \item Systems Programming in C/C++ : 92\%
        \item Functional Programming : 100\%
        \item Team Project : 78\%
    \end{itemize}}
    Final year modules:
    \begin{itemize}
        \item Security of Real-World Systems
        \item Advanced Networking
        \item Computer Vision and Imaging
        \item Intelligent Interactive Systems
        \item Computer Science Project
    \end{itemize}
    
    \CVItem{St Ambrose College (2012-2019)}{ \textbf{A-Levels} \\
    Mathematics (A*), Computer Science (A), Chemistry (A) \\}

    \CVHeading{Interests}
    I enjoy all sports and played rugby union as well as league at school, university and club. I took part in tours to Ireland and to Australia. I keep in shape by going to the gym, running and bike riding. I am currently in the process of completing my Duke of Edinburgh gold course. I also enjoy cooking and gardening, volunteering for the conservation group which works on projects to grow a vegetable garden and maintain habitats around the Midlands. 
\end{document}